---
title: "20180601_Chemotaxis"
author: "Tim C."
date: "6/1/2018"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

### Notes
Chemotaxis data are from three blocks. Each block contained 11 strains, three replicate plates per strain. Worms were transfered for 3 generations prior to bleach synchronization and grown to L4 stage prior to experiment. Worms were then washed off four 60 mm plates (~1,500 worms/plate) with M9 and sorted to 60 mm chemotaxis plates (50 worms in 50 ul). Test and control spots contained 2.5 ul and were loaded using the version2 plate template from Zeke. Excess liquid was either removed with kimwipe or left to dry on its own for ~10-15 min prior to chemotaxis. Worms were left to chemotax for 1 h at 20 C then plates were transfered to 4C. 24 -72 h later worms were imaged by Chido and manually counted using imageJ cell counter plugin. Cropped images were also used to count nemtodes with automated Python package `chemotaxis-cli`. 

```{r, echo=F, warning = F, message=F}
library(tidyverse)
library(scales)
try(setwd(dirname(rstudioapi::getActiveDocumentContext()$path)))
```

### Read in data
```{r, echo = FALSE, warning=FALSE}
df <- as.data.frame(read.csv(file = glue::glue("{getwd()}/../data/Results_Block_3_4_6b_8.csv"), header = T))


df <- df%>%
  dplyr::select(-X, -X.1, -X.2) %>%
  dplyr::filter(CI != "#DIV/0!") %>%
  dplyr::filter(strain != "ED3017") %>%
  dplyr::filter(!is.na(Assay),
                Assay != "20180307") %>% #filter block 20180307
  dplyr::mutate(CI = as.numeric(as.character(CI)),
                drug = ifelse(drug == "isa", "isoamly alcohol", "1-octanol"))

glimpse(df)


# define heritability test
H2.test <- function(data){
  
  pheno <- as.data.frame(dplyr::select(data, phenotype))[,1]
  strain <- as.factor(data$strain)
  
  reffMod <- lme4::lmer(pheno ~ 1 + (1|strain))
  
  Variances <- as.data.frame(lme4::VarCorr(reffMod, comp = "Variance"))
  
  Vg <- Variances$vcov[1]
  Ve <- Variances$vcov[2]
  H2 <- Vg/(Vg+Ve)
  
  return(H2)
}



```

### CI Plots
```{r, echo = FALSE, warning=FALSE}
# Plotting CI manual counts

fig1 <- ggplot(df %>% dplyr::filter(counter == "manual")) +
  aes(x = strain, y = CI) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(color = as.factor(Assay)), width = .25, alpha = 0.75, size = 2)+
  ylim(-1,1) +
  facet_grid(~drug) +
  theme_classic() +
   theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black")) + 
  labs(title = "FIG 1: Manual counting", color = "Block", x = "", y = "Chemotactic Index (ci)") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  theme(legend.position="right")
fig1

ggsave('fig1_manual_CI.pdf', width = 12, height = 8)
ggsave('fig1_manual_CI.png', width = 12, height = 8)

# Plotting automated counts

fig2 <- ggplot(df %>% dplyr::filter(counter == "auto")) +
  aes(x = strain, y = CI) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(color = as.factor(Assay)), width = .25, alpha = 0.75, size = 2)+
  facet_grid(~drug) +
  ylim(-1,1) +
  theme_classic() +
   theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black")) + 
  labs(title = "FIG 2: Automated counting", color = "Block", x = "", y = "Chemotactic Index (ci)") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  theme(legend.position="right")
fig2

ggsave('fig2_auto_CI.pdf', width = 12, height = 8)
ggsave('fig2_auto_CI.png', width = 12, height = 8)

# correlation between manual and auto
lm_eqn <- function(df){
    m <- lm(auto_ci ~ man_ci, df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 2), 
              b = format(coef(m)[2], digits = 2), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}
```

### Method correlation
```{r, echo=FALSE, warning=FALSE}
# Fitting correlation with ggplot to two compopunds manual counts vs. automated counts
df_corr <- df %>%
  dplyr::select(-Drug_Count, -Control_Count, -count) %>%
  tidyr::spread(counter, CI) %>% 
  dplyr::rename(man_ci = manual, auto_ci = auto)

# Add two linear regression plots red = #F8766D, blue = #00BFC4
# show_col(hue_pal()(2))

fig3 <- ggplot() +
  geom_point(data = df_corr %>% dplyr::filter( drug == "1-octanol"), aes(x = man_ci, y = auto_ci, color = as.factor(drug))) +
  geom_smooth(data = df_corr %>% dplyr::filter(drug == "1-octanol"), aes(x = man_ci, y = auto_ci), method=lm, color = "#F8766D", size = 0.5) +
  geom_text(data = df_corr %>% dplyr::filter( drug == "1-octanol"), x = -.45, y = 0.4, label = lm_eqn(df_corr %>% dplyr::filter(drug == "1-octanol")), parse = TRUE, check_overlap = TRUE, color = "#F8766D", size = 5) +
  geom_point(data = df_corr %>% dplyr::filter( drug == "isoamly alcohol"), aes(x = man_ci, y = auto_ci, color = as.factor(drug))) +
  geom_smooth(data = df_corr %>% dplyr::filter(drug == "isoamly alcohol"), aes(x = man_ci, y = auto_ci), method=lm, color = "#00BFC4", size = 0.5) +
  geom_text(data = df_corr %>% dplyr::filter( drug != "1-octanol"), x = .45, y = -0.4, label = lm_eqn(df_corr %>% dplyr::filter(drug != "1-octanol")), parse = TRUE, check_overlap = TRUE, color = "#00BFC4", size = 5) +
  xlim(-1,1) +
  ylim(-1,1) +
   theme_light() +
   theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black")) + 
  labs(title = "FIG 3: Assay agreement", color = "drug", x = "Manual (CI)", y = "Automated (CI)") +
  theme(legend.position="right")
fig3

ggsave('fig3_assay_agreement_CI.pdf', width = 12, height = 8)
ggsave('fig3_assay_agreement_CI.png', width = 12, height = 8)


```

### Heritability Calculations
```{r, echo=FALSE, warning=FALSE}
# Calculate heritability including three replicates per block
h2_df_full<- df %>%
  dplyr::rename(trait = drug, phenotype = CI) %>%
  dplyr::select(-Drug_Count, -Control_Count, -Image_ID) %>% 
  dplyr::mutate(strain = as.character(strain)) %>%
  dplyr::arrange(counter, trait, strain)

# export heritability dataframe
#rio::export(h2_df_full, "chemotaxis_heritability_dataframe.csv")

h2_df<- h2_df_full %>%
  dplyr::group_by(counter, trait) %>%
  dplyr::do(broom::tidy(H2.test(.))) %>%
  dplyr::rename(H2 = x) %>%
  dplyr::ungroup()

fig4 <- ggplot() +
  geom_point(data = h2_df, aes(x = trait, y = H2, color = counter)) +
  #geom_point(data = h2_df %>% dplyr::filter(counter == "auto"), aes(x = trait, y = H2)) +
  #geom_point(data = h2_df %>% dplyr::filter(counter == "manual"), aes(x = trait, y = H2)) +
  ylim(0,1) +
  geom_line(aes(x = c(0,3), y = 0.2), linetype="dashed", color="black") +
  theme_light() +
   theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black")) + 
  labs(title = "FIG 4: Heritability for three replicates per block", color = "Method", x = "", y = "H2") +
  theme(legend.position="right")
fig4

#ggsave('fig4_h2_reps.pdf', width = 12, height = 8)
#ggsave('fig4_h2_reps.png', width = 12, height = 8)

# Calculate heritability with replicates averaged per block
h2_df_2<- df %>%
  dplyr::group_by(Assay, drug, strain, counter) %>%
  dplyr::mutate(mean_CI = mean(CI)) %>%
  dplyr::distinct(Assay, counter, strain, drug, .keep_all = T) %>%
  dplyr::rename(trait = drug, phenotype = mean_CI) %>%
  dplyr::select(-Drug_Count, -Control_Count, -Image_ID, -CI) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(strain = as.character(strain)) %>%
  dplyr::group_by(counter, trait) %>%
  dplyr::do(broom::tidy(H2.test(.))) %>%
  dplyr::rename(H2 = x) %>%
  dplyr::ungroup()

fig5 <- ggplot() +
  geom_point(data = h2_df_2, aes(x = trait, y = H2, color = counter), size = 3) +
  #geom_point(data = h2_df %>% dplyr::filter(counter == "auto"), aes(x = trait, y = H2)) +
  #geom_point(data = h2_df %>% dplyr::filter(counter == "manual"), aes(x = trait, y = H2)) +
  ylim(0,1) +
  geom_line(aes(x = c(0,3), y = 0.2), linetype="dashed", color="black") +
  theme_light() +
   theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black")) + 
  labs(title = "FIG 5: Heritability for block means", color = "Method", x = "", y = "H2") +
  theme(legend.position="right")
fig5

#ggsave('fig5_h2_means.pdf', width = 12, height = 8)
#ggsave('fig5_h2_means.png', width = 12, height = 8)

```

###Spearman's rank order testing for blocks
```{r, echo=FALSE, warnings=FALSE}
df_rank <- df %>%
  dplyr::group_by(Assay, drug, strain, counter) %>%
  dplyr::mutate(mean_CI = mean(CI)) %>%
  dplyr::distinct(Assay, counter, strain, drug, .keep_all = T) %>%
  dplyr::group_by(Assay, drug, counter) %>%
  dplyr::mutate(r_CI = rank(CI),
                scaledr_CI = scales::rescale(r_CI, to = range(CI))) %>%
  dplyr::select(Assay, counter, strain, drug, CI) %>%
  tidyr::spread(Assay, CI) %>%
  dplyr::rename("block_1" = `20180321`, "block_2" = `20180420`, "block_3" = `20180508`) %>%
  dplyr::group_by(counter, drug) %>%
  dplyr::mutate(b1_V_b2 = cor(block_1, block_2, method = "spearman"),
                b1_V_b3 = cor(block_1, block_3, method = "spearman"),
                b2_V_b3 = cor(block_2, block_3, method = "spearman")) %>%
  dplyr::distinct(counter, drug, .keep_all = T) %>%
  tidyr::gather(cor, value, b1_V_b2, b1_V_b3, b2_V_b3) %>%
  dplyr::select(-strain, -block_1, -block_2, -block_3)

cor_plot <- ggplot(df_rank) +
  aes(x = cor, y = value, color = counter) +
  geom_point(size = 3) +
  facet_wrap(~drug)+
  theme_light() +
   theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "FIG 4: Spearman's rank correlation", x = "", y = "Spearman's rho", color = "Method") +
  theme(legend.position="right")
cor_plot

#ggsave('fig6_rank_order.pdf', width = 12, height = 8)
#ggsave('fig6_rank_order.png', width = 12, height = 8)
```
 
### Plots of rank order
```{r, echo=FALSE, warning=FALSE}
# Function for flagging outliers (used 2.5 * IQR)
flag_outliers <- function(x, na.rm = TRUE, ...) {
  qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
  H <- 2.5 * IQR(x, na.rm = na.rm)
  y <- x
  y[x < (qnt[1] - H)] <- "TRUE"
  y[x > (qnt[2] + H)] <- "TRUE"
  y[x > (qnt[1] - H) & x < (qnt[2] + H)] <- "FALSE"
  y
  }

#remove flagged outliers then take mean of replicates within blocks
df_proc_ranks <- df %>%
  dplyr::group_by(counter, strain, drug) %>%
  dplyr::mutate(CI_outlier = flag_outliers(CI)) %>%
  dplyr::filter(CI_outlier != "TRUE") %>%
  dplyr::group_by(Assay, drug, strain, counter) %>%
  dplyr::mutate(mean_CI = mean(CI))
  
#plot CI by block and method
df_proc_ranks_plot_a <- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180321", counter == "auto", drug == "1-octanol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 1: 1-octanol", x = "", y = "CI", color = "") +
  theme(legend.position="none")

df_proc_ranks_plot_a
          
df_proc_ranks_plot_b<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180321", counter == "auto", drug == "isoamly alcohol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 1: isoamyl alcohol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_b

df_proc_ranks_plot_c<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180420", counter == "auto", drug == "1-octanol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 2: 1-octanol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_c

df_proc_ranks_plot_d<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180420", counter == "auto", drug == "isoamly alcohol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 2: isoamyl alcohol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_d

df_proc_ranks_plot_e<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180508", counter == "auto", drug == "1-octanol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 3: 1-octanol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_e

df_proc_ranks_plot_f<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180508", counter == "auto", drug == "isoamly alcohol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 3: isoamyl alcohol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_f

#test <- cowplot::plot_grid(df_proc_ranks_plot_a, df_proc_ranks_plot_b, df_proc_ranks_plot_c, df_proc_ranks_plot_d, df_proc_ranks_plot_e, df_proc_ranks_plot_f, ncol = 2, nrow = 3, align = "vh")
#test

#ggsave('fig7_rank_auto.pdf', width = 24, height = 16)
#ggsave('fig7_rank_auto.png', width = 24, height = 16)

# Plot manual count ranks too

df_proc_ranks_plot_a <- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180321", counter == "manual", drug == "1-octanol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 1: 1-octanol", x = "", y = "CI", color = "") +
  theme(legend.position="none")

df_proc_ranks_plot_a
          
df_proc_ranks_plot_b<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180321", counter == "manual", drug == "isoamly alcohol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 1: isoamyl alcohol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_b

df_proc_ranks_plot_c<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180420", counter == "manual", drug == "1-octanol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 2: 1-octanol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_c

df_proc_ranks_plot_d<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180420", counter == "manual", drug == "isoamly alcohol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 2: isoamyl alcohol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_d

df_proc_ranks_plot_e<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180508", counter == "manual", drug == "1-octanol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 3: 1-octanol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_e

df_proc_ranks_plot_f<- 
  ggplot(df_proc_ranks %>% dplyr::filter(Assay == "20180508", counter == "manual", drug == "isoamly alcohol")) +
  #geom_boxplot(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI)) +
  geom_point(aes(x = forcats::fct_reorder(strain, mean_CI), y = CI), size = 3, alpha = .5) +
  theme_light() +
  ylim(-1,1) +
  theme(title = element_text(size = 16, color = "black", face = "bold"),
        axis.title = element_text(size = 16, color = "black", face = "bold"),
        axis.text = element_text(size = 16, color = "black"),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.x = element_text(size = 16, colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "block 3: isoamyl alcohol", x = "", y = "CI", color = "") +
  theme(legend.position="none")
df_proc_ranks_plot_f

test_manual <- cowplot::plot_grid(df_proc_ranks_plot_a, df_proc_ranks_plot_b, df_proc_ranks_plot_c, df_proc_ranks_plot_d, df_proc_ranks_plot_e, df_proc_ranks_plot_f, ncol = 2, nrow = 3, align = "vh")

#ggsave('fig7_rank_manual.pdf', width = 24, height = 16)
#ggsave('fig7_rank_manual.png', width = 24, height = 16)

# calculate spearman's rho for outlier filtered data
df_proc_rank_cor <- df_proc_ranks %>%
  dplyr::select(Assay, counter, strain, drug, CI) %>%
  tidyr::spread(Assay, CI) %>%
  dplyr::rename("block_1" = `20180321`, "block_2" = `20180420`, "block_3" = `20180508`) %>%
  dplyr::group_by(counter, drug) %>%
  dplyr::mutate(b1_V_b2 = cor(block_1, block_2, method = "spearman"),
                b1_V_b3 = cor(block_1, block_3, method = "spearman"),
                b2_V_b3 = cor(block_2, block_3, method = "spearman")) %>%
  dplyr::distinct(counter, drug, .keep_all = T) %>%
  tidyr::gather(cor, value, b1_V_b2, b1_V_b3, b2_V_b3) %>%
  dplyr::select(-strain, -block_1, -block_2, -block_3)

#ggsave('fig.pdf', width = 12, height = 8)
#ggsave('fig.png', width = 12, height = 8)
```
